Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
The use of power generation with renewable energy sources is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems. We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is infeasible. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\end{abstract}

@@

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via model checking with a lower bound that serves as the minimum cost of reference. If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}. Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools. Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems. We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst. Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.

>>>>

\begin{abstract}
The use of power generation with renewable energy sources is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems. We use a stand-alone configuration for this study since it is the most common system used for remote rural areas of developing countries or areas where the grid extension is infeasible. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Automated Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via software model checking with a lower bound that serves as the minimum cost of reference. If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}. Here the application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools. Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems. We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst. Lastly, we discuss the challenges of applying software verification to PV systems and reflect on lessons learned from this experience.
